Unsupervised training of maximum-entropy models for lexical selection in rule-based machine translation

### 2015-02-10 2015-eamt-melsa/2015-eamt-melsa.tex
trimming
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58813 72bbbca6-d526-0410-a7d9-f06f51895060

For creating the test corpora, and for providing a source language corpus 
for training, and a target language corpus for scoring, we used four parallel corpora: 
\begin{itemize}
\addtolength{\itemsep}{-0.10in}
\item \textbf{Ofis ar Brezhoneg} (\texttt{OAB}): This parallel corpus
  of Breton and French has been collected specifically for
  lexical-selection experiments from translations produced by
  \emph{Ofis ar Brezhoneg} `The Office of the Breton
  language'.%\footnote{In 2010 the administrative status was changed
%    and it was renamed \emph{Ofis Publik ar Brezhoneg} `Public office
%    of the Breton language'. The corpus was published before this date
%    so we use the original name.}  
  It contains some parallel data
  previously described in \cite{tyers09b}, and also some new data. The
  corpus has been made available online through {\sc opus}.\footnote{\url{http://opus.lingfil.uu.se}}
\item \textbf{South-East European Times} (\texttt{SETimes}): Described
  in \cite{tyers10}, this corpus is a multilingual corpus of the
  Balkan languages in the news domain. The Macedonian and English
  portion will be used.
\item \textbf{Open Data Euskadi} (\texttt{OpenData}): This is a Basque
  and Spanish parallel corpus made from the translation memories of
  the \emph{Herri Arduralaritzaren Euskal Erakundea} `Basque Institute
  of Public
  Administration'.\footnote{\url{http://opendata.euskadi.net/w79-contdata/es/contenidos/ds_recursos_linguisticos/memorias_traduccion/es_izo/memorias_traduccion_izo.html}}
\item \textbf{European Parliament Proceedings} (\texttt{EuroParl}):
  Described by \cite{koehn05a}, this is a multilingual corpus of the
  European Union official languages. We are using the English--Spanish
  data from version 7.
\end{itemize}

There are a number of approaches to creating evaluation corpora for
lexical selection in the literature. \cite{vickrey05} use a parallel
corpus to make annotated test and training sets for experiments in
lexical selection applied to a simplified translation problem in
SMT. They use word alignments from {\sc giza++} \citep{och03a} to
annotate source language words with their translations from the
reference translation in the parallel corpus. One disadvantage of this
method is that only one translation is annotated per source language
word, meaning that accuracies may be lower because of missing
translations --- this happens when the system chooses a translation
which is adequate, but is not found in the reference translation. A
second disadvantage is that the word alignments may not be 100\%
reliable, which decreases the accuracy of the annotated corpus. An
alternative method is described by \cite{zinovjeva2000}, who manually
tags a selection of ambiguous words in English sentences with their
translation in Swedish. The size of the annotated corpus is not
mentioned. 
%\cite{specia2005a} use a parallel corpus, but eschew using
%word alignment in favour of using a bilingual dictionary and heuristic
%rules based on part-of-speech and relative position. The corpus was
%reviewed manually before being used in further experiments
%\citep{specia2005}.

@@

Improvements with
 respect to the target-language-model performance are very likely due
 to the effective use the maximum-entropy model makes of information
 about the relevant source-language contexts and their translations,
 through the weighting of features representing those source-language
 contexts across the whole training corpus.

>>>>

For creating the test corpora, and for providing a source language corpus 
for training, and a target language corpus for scoring, we used four parallel corpora: 
\begin{itemize}
\addtolength{\itemsep}{-0.10in}
\item \textbf{Ofis ar Brezhoneg} (\texttt{OAB}): This parallel corpus
  of Breton and French has been collected specifically for
  lexical-selection experiments from translations produced by
  \emph{Ofis ar Brezhoneg} `The Office of the Breton
  language'.%\footnote{In 2010 the administrative status was changed
%    and it was renamed \emph{Ofis Publik ar Brezhoneg} `Public office
%    of the Breton language'. The corpus was published before this date
%    so we use the original name.}  
%  It contains some parallel data
%  previously described in \cite{tyers09b}, and also some new data. 
The corpus has been made available online through {\sc opus}.\footnote{\url{http://opus.lingfil.uu.se}}
\item \textbf{South-East European Times} (\texttt{SETimes}): Described
  in \cite{tyers10}, this corpus is a multilingual corpus of the
  Balkan languages in the news domain. The Macedonian and English
  portion will be used.
\item \textbf{Open Data Euskadi} (\texttt{OpenData}): This is a Basque
  and Spanish parallel corpus made from the translation memories of
  the \emph{Herri Arduralaritzaren Euskal Erakundea} `Basque Institute
  of Public
  Administration'.\footnote{\url{http://opendata.euskadi.net/w79-contdata/es/contenidos/ds_recursos_linguisticos/memorias_traduccion/es_izo/memorias_traduccion_izo.html}}
\item \textbf{European Parliament Proceedings} (\texttt{EuroParl}):
  Described by \cite{koehn05a}, this is a multilingual corpus of the
  European Union official languages. We are using the English--Spanish
  data from version 7.
\end{itemize}

There are a number of approaches to creating evaluation corpora for
lexical selection in the literature. \cite{vickrey05} use a parallel
corpus to make annotated test and training sets for experiments in
lexical selection applied to a simplified translation problem in
SMT. They use word alignments from {\sc giza++} \citep{och03a} to
annotate source language words with their translations from the
reference translation in the parallel corpus. One disadvantage of this
method is that only one translation is annotated per source language
word, meaning that accuracies may be lower because of missing
translations --- this happens when the system chooses a translation
which is adequate, but is not found in the reference translation. A
second disadvantage is that the word alignments may not be 100\%
reliable, which decreases the accuracy of the annotated corpus. An
alternative method is described by \cite{zinovjeva2000}, who manually
tags a selection of ambiguous words in English sentences with their
translation in Swedish. %The size of the annotated corpus is not
%mentioned. 
%\cite{specia2005a} use a parallel corpus, but eschew using
%word alignment in favour of using a bilingual dictionary and heuristic
%rules based on part-of-speech and relative position. The corpus was
%reviewed manually before being used in further experiments
%\citep{specia2005}.

@@

Improvements with
 respect to the target-language-model performance are likely due
 to the effective use the maximum-entropy model makes of information
 about the relevant source-language contexts and their translations,
 through the weighting of features representing those source-language
 contexts across the whole corpus.
